---
title: "Final Project"
author: "Mohan Rajendran"
date: "12/12/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Amazon Reviews
In this problem, you will use R to do further analysis on the Amazon reviews data.  Where relevant, you are encouraged to use functions from `dplyr` and `ggformula`.

Load necessary libraries here.
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(magrittr)
library(dplyr)
library(readr)
library(ggformula)
library(stringr)
library(png)
library(grid)
```

### Reading and cleaning the data

```{r}
Friends_All_df <- read_csv(file="Friends_All_Tweet_Data.csv", col_names=TRUE)
head(Friends_All_df)

```

### Computing data frames for use in chi test and t-test

```{r}
Friends_All_df <- Friends_All_df %>%
  mutate(created_at_modified = substring(Friends_All_df$created_at, 1, 10))
Friends_All_df

Friends_All_Daily_Count_df <- Friends_All_df %>%
  group_by(created_at_modified, Character) %>%
  summarize(count = n())
Friends_All_Daily_Count_df

Friends_All_Count_df <- Friends_All_df %>%
  group_by(Character) %>%
  summarize(count = n())
Friends_All_Count_df

```

### Chi Square goodness of fit will let us know whether the characters are mentioned in same frequencies

```{r}

res <- chisq.test(Friends_All_Count_df$count, p = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6))
res

```



```{r}

img <- readPNG("Friends.png")
g <- rasterGrob(img, interpolate=TRUE)

ggplot(Friends_All_Count_df, aes(x = reorder(Character, count), count, fill = Character), y = count) +
        
        geom_bar(stat = "identity") +
        annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=1000)+
        ggtitle("Friends Characters Frequency Chart")+
        xlab("Character") + ylab("Count")

```

### It is evident from the p value of less than the machine epsilon of 0.00000000000000022  that the frequencies of tweets for the six characters are not equally distributed

### Two Sample t-test are performed to understand whether chandler mentions in the tweets are more than the other charcters.

```{r}
compute_t_test <- function(df, character1, character2){
  ##This function will accept the dataframe and two character names and compute the t-test between them
  chr1_df <- filter(df, Character == character1 )
  chr2_df <- filter(df, Character == character2)
  res <- t.test(chr1_df$count, chr2_df$count, alternative = "greater")
  return(res)
  
}

print_t_test_outcome <- function(p_value,  Character1, Character2){
  if (p_value < 0.05){
  print(paste0("With p value of ", p_value, " it is safe to say there is statistically significant evidence that the frequency of tweets about ", Character1, " is greater than the tweets towards ", Character2))
} else {
  print(paste0("With p value of ", p_value, " it is safe to say there is no statistically significant evidence that the frequency of tweets about ", Character1, " is greater than the tweets towards ", Character2))
}
}

```

The hypothesis for the two sample t test with alternative = greater is as follows
H0: u1 - u2 = 0
Ha: u1 - u2 > 0

```{r}

Character1 = 'Chandler'
Character2 = 'Ross'
res <- compute_t_test(Friends_All_Daily_Count_df, Character1, Character2)
print_t_test_outcome(res$p.value, Character1, Character2)

```



```{r}
Character1 = 'Chandler'
Character2 = 'Joey'
res <- compute_t_test(Friends_All_Daily_Count_df, Character1, Character2)
print_t_test_outcome(res$p.value, Character1, Character2)
```



```{r}
Character1 = 'Chandler'
Character2 = 'Monica'
res <- compute_t_test(Friends_All_Daily_Count_df, Character1, Character2)
print_t_test_outcome(res$p.value, Character1, Character2)
```



```{r}
Character1 = 'Chandler'
Character2 = 'Phoebe'
res <- compute_t_test(Friends_All_Daily_Count_df, Character1, Character2)
print_t_test_outcome(res$p.value, Character1, Character2)
```



```{r}
Character1 = 'Chandler'
Character2 = 'Rachel'
res <- compute_t_test(Friends_All_Daily_Count_df, Character1, Character2)
print_t_test_outcome(res$p.value, Character1, Character2)
```

### Compared to all the characters, Rachel is more close to Chandler in twitter mentions

